Generate data for NOBA cod ensemble modeling

### 2020-03-25 NOBAcod.Rmd
add wt age plot

```{r}

>>>>

```{r wtage}

annwtage <- weightage %>%
  group_by(species, agecl, time) %>%
  summarise(wtage = mean(atoutput)) %>%
  filter(time %in% survtime)

wageplot <- ggplot(annwtage, aes(time, wtage)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (5 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year sample"))

wageplot + facet_wrap(c("species"), scales="free_y")
